Notes on modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating doc

>>>>

In seeking to apply \gmvp{} to select \qnm{} frequencies, we wish to impose a zero-damping constraint, namely that some frequencies are real as $\jf \rightarrow 1$.
We also wish the impose a domain transformation, $\kappa(\jf)$, such that $0 \leq \kappa \leq 1$ and the individual \qnm{} frequencies are morphologically simplified.
\par For the domain transformation, inspection of \qnm{} frequencies with $\ell \leq 5$ suggest that
  \kappa(\jf) = \left( \ln( 2 - \jf ) / \ln(3) \right)^{1/(2-\ell+|m|)}
appropriately linearizes the sharp behavior of each frequency near $\jf=1$.
  \cw_{\lmn} = m/2 + \kappa \sum_{j=1}^{J} c_j \kappa^k
In the case of the non-zero damped \qnm{s}, (e.g. $(\ell,m)=(3,2)$), a more general polynomial form may be adopted, namely,
  \cw_{\lmn} = \sum_{j=0}^{J} c_j \kappa^k
\par For the zero-damping constraint, when considering a \qnm{} frequency $\cw_{\lmn}$, zero-damping at $\jf=1$ implies that $\cw_{\lmn}(\kappa \approx 0)-m/2 \propto \kappa$, where $m/2$ is the well known limiting value for each \qnm{} frequencies real part as $\jf\rightarrow 1$.
